The fulfillment of the project requires a list of tasks to be completed in the order they are presented here, it is important to note, however that this list of tasks is intended to be used as a general guideline and all the tasks may receive updates along the way.
Small changes can be made to the order, especially the last two and the first two steps that will be re-iterated over and over as new requirements emerge.
So, the first version of each task will have strict deadlines, so that the following task can start, while the re-iterations will have specific deadlines that will be specified along the process.

Here is the a table that summirises the main tasks to be completed:
\begin{center}
\begin{tabular}{ |c|l| } \hline
	\textbf{Order} & \textbf{Task} \\ \hline
	1 & RASD \\ \hline
	2 & DD \\ \hline
	3 & ITPD \\ \hline
	4 & PPD \\ \hline
	5 & Code Inspection \\ \hline
\end{tabular}
\end{center}

Here we explain what each task is for:

\begin{enumerate}
	\item Prepare a document that specifies the goals of the system, the assumptions that had been made, and the requirements of the \emph{system-to-be}, namely the RASD.
	\item Prepare a document that specifies the design and architecture of the \emph{system-to-be}, namely the DD.
	\item Prepare a document that specifies the plan to follow in order to perform the integration testing, namely the ITPD.
	\item Prepare a document that specifies the plan of the project, namely the PPD.
	\item Perform the Code inspection from the material that professors gave us.
\end{enumerate}

\subsection{Schedule} % (fold)
\label{sub:schedule}

In this subsection we present a schedule that must followed, however, as always, small changes can always be made.

We explain the schedule through the Gantt chart that follows:

% ZAN ZAN ZANNNNNNNNNNNNNNNNNN
%
%
%
%
%
%
%
%
%
%
%
%
%
% DA FARE (FORSE) (SE GIANNI VUOLE) 

% subsection schedule (end)

Since the precise deadlines are not legible from the Gantt chart, we give also a table summarising the main deadlines.

\begin{center}
\begin{tabular}{ |c|c|l|c| } \hline
	\textbf{Order} & \textbf{Start date} & \textbf{Task} & \textbf{Deadline} \\ \hline
	1 & 20-10-2016 & RASD & 13-11-2016 \\ \hline
	2 & 16-11-2015 & DD & 11-12-2016 \\ \hline
	3 & 18-12-2016 & ITPD & 15-01-2017 \\ \hline
	4 & 27-12-2016 & PPD & 22-01-2017 \\ \hline
	5 & 16-01-2017 & Code inspection  & 05-02-2017 \\ \hline
\end{tabular}
\end{center}


\newpage




In this section we specifiy the resource allocation, that is, for each task we specify to whom its subtasks are allocated. The timetables have already been defined in section \ref{sub:schedule}.
We choose to represent this data by means of tables. As far as the documents are concerned, we specify the resources for each section of the document, whereas, for what concerns the \emph{Implementation + Unit Testing} we provide a resource for each of the three main applications that will have to be developed. Of course also this allocation can be subject to small changes in the future.

\begin{center}
\begin{tabular}{ |l|l| }
	\multicolumn{2}{c}{\textbf{RASD}} \\ \hline
	\textbf{Subtask} & \textbf{Resource} \\ \hline
	\multirow{3}{*}{Introduction} & Simone \\
										& Claudia \\
										& Yannick \\ \hline
	\multirow{3}{*}{Overall Description} & Simone \\
										& Claudia \\
										& Yannick \\ \hline
	\multirow{3}{*}{Specific Requirements} & Simone \\
										& Claudia \\
										& Yannick \\ \hline
	\multirow{3}{*}{Appendices} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline

\end{tabular}
\end{center}

\vspace* {30px}


\begin{center}
\begin{tabular} {|l|l|}
	\multicolumn{2}{c}{\textbf{DD}} \\ \hline
	\textbf{Subtask} & \textbf{Resource} \\ \hline
	\multirow{3}{*}{Introduction} & Simone \\
								 & Claudia \\
								 & Yannick \\ \hline
	\multirow{2}{*}{Architectural Design} & Simone \\
										  &	Yannick \\ \hline
	\multirow{2}{*}{Algorithm Design} & Simone \\
									& Claudia \\ \hline
	\multirow{2}{*}{User Interface Design} & Claudia \\
				& Yannick \\ \hline
	\multirow{3}{*}{Requirements Traceability} & Simone \\
											   & Claudia \\
											   & Yannick \\ \hline
	\multirow{3}{*}{Appendices} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline
\end{tabular}
\end{center}

\vspace* {30px}

\begin{center}
\begin{tabular}{ |l|l| }
	\multicolumn{2}{c}{\textbf{ITPD}} \\ \hline
	\textbf{Subtask} & \textbf{Resource} \\ \hline
	\multirow{3}{*}{Introduction} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline
	\multirow{3}{*}{Integration Strategy} & Simone \\ 
									& Claudia \\
									& Yannick \\ \hline
	\multirow{1}{*}{Individual Steps and Test Description} & Yannick \\ \hline
	\multirow{1}{*}{ Tool and Test Equipment Required } & Claudia \\ \hline
	\multirow{1}{*}{Program Stubs and Data Test Required} & Simone \\ \hline
	\multirow{3}{*}{Appendices} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline

\end{tabular}
\end{center}

\vspace* {30px}

\begin{center}
\begin{tabular}{ |l|l| }
	\multicolumn{2}{c}{\textbf{PPD}} \\ \hline
	\textbf{Subtask} & \textbf{Resource} \\ \hline
	\multirow{3}{*}{Introduction} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline
	\multirow{2}{*}{Size, Effort and Cost Estimation} & Simone \\ 
									& Claudia \\ \hline
	\multirow{3}{*}{Schedule and Resourse Allocation} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline
	\multirow{1}{*}{Project Risks} & Yannick \\ \hline
	\multirow{3}{*}{Appendices} & Simone \\ 
				& Claudia \\
				& Yannick \\ \hline

\end{tabular}
\end{center}


\vspace* {30px}

\begin{center}
\begin{tabular}{ |l|l| }
	\multicolumn{2}{c}{\textbf{Code Inspection}} \\ \hline
	\textbf{Subtask} & \textbf{Resource} \\ \hline
	\multirow{1}{*}{...} & Simone \\ \hline
	\multirow{1}{*}{...} & Claudia \\ \hline
	\multirow{1}{*}{...} & Yannick \\ \hline


\end{tabular}
\end{center}