\subsection{Program Stubs}
\begin{itemize}
\item If not already present, a test database consistent with a future implementation, should be created as to test read/write operations to and from a database.
\item In the test suite \hyperref[sub:IT11]{I11} a \textbf{code stub} that simulates a Client's application's behaviour is required as to send valid and consistent HTTPS requests to the RESTful API. 
\item Code stubs must be used each time that involves a module which is not fully developed yet.
\end{itemize}

\subsection{Test Data}
\begin{itemize}
\item \hyperref[sub:IT1]{I1}, \hyperref[sub:IT2]{I2} and \hyperref[sub:IT3]{I3}  need a some \textbf{Request} to test different scenarios.
\item \hyperref[sub:IT4]{I4} needs a valid \textbf{search request} with valid parameters to be handled.
\item \hyperref[sub:IT5]{I5} needs a valid \textbf{vehicle} object with correct parameters and a its relative vehicle manager.
\item \hyperref[sub:IT6]{I6} needs some \textbf{test objects} to input to the database through queries
\item \hyperref[sub:IT7]{I7} needs a Request to be send to the Request Manager.
\item \hyperref[sub:IT8]{I8} needs a Ride Object able to send out messages to a client mock.
\item \hyperref[sub:IT9]{I9} needs Search data that must be interpreted by the Position manager and send out a response to the client mock through the Notification Manager.
\item \hyperref[sub:IT10]{I10} needs a fictional message object to send to the mock client
\item \hyperref[sub:IT11]{I11} needs different type of request via consistent and proper data according to the type of request.
\end{itemize}