%Issue list for Yannick

\subsubsection{Object Comparison}
\begin{itemize}
\item Line 66 : '==' used instead of \texttt{equals} on a \texttt{ShoppingCart} object.
\item Line 74 : '==' used instead of \texttt{equals} on a \texttt{ShoppingCart} object.
\item Line 80 : '==' used instead of \texttt{equals} on a \texttt{List}.
\item Line 85 : '==' used instead of \texttt{equals} on a \texttt{List}.
\item Line 109 : '==' used instead of \texttt{equals} on a \texttt{Iterator}.
\item Line 118: '==' used instead of \texttt{equals} on a \texttt{String}.
\item Line 127 : '==' used instead of \texttt{equals} on a \texttt{List}.
\item Line 61 : '==' used instead of \texttt{equals} on a \texttt{String}.
\item Line 154 : '==' used instead of \texttt{equals} on a \texttt{GenericValue}.
\item Line 155 : '==' used instead of \texttt{equals} on a \texttt{GenericValue}.
\item Line 162 : '==' used instead of \texttt{equals} on  \texttt{Maps}.
\item Line 172 : '==' used instead of \texttt{equals} on a \texttt{Iterator}.
\item Line 178 : '==' used instead of \texttt{equals} on a \texttt{Iterator}.
\item Line 189 : '==' used instead of \texttt{equals} on a \texttt{BigDecimal}.
\item Line 192 : '==' used instead of \texttt{equals} on a \texttt{BigDecimal}.
\item Line 189 : '==' used instead of \texttt{equals} on a \texttt{BigDecimal}.
\item Line 197 : '==' used instead of \texttt{equals} on a \texttt{Integer}.
\item Line 288 : '==' used instead of \texttt{equals} on a \texttt{List}.
\item Line 289 : '==' used instead of \texttt{equals} on a \texttt{Integer}.
\item Line 322 : '==' used instead of \texttt{equals} on  \texttt{Objects}.
\item Line 328 : '==' used instead of \texttt{equals} on a \texttt{Object}.
\end{itemize}
\subsubsection{Output Format}
\begin{itemize}
\item No issues found.
\end{itemize}
\subsubsection{Computation , Comparisons and Assignments}
\begin{itemize}
\item Line 141: return \texttt{cartAssocs} would have sufficed.
\item Line 208: division by 0 could occur.
\item Line 280: wrong Exception handling
\end{itemize}
\subsubsection{Exceptions}
\begin{itemize}
\item Line 280: wrong Exception handling. Debugger used instead of error solving.
\end{itemize}
\subsubsection{Flow Control}
\begin{itemize}
\item All for and while loops are well formed.
\end{itemize}
\subsubsection{Files}
\begin{itemize}
\item No issues found
\end{itemize}
