This section analyses the meaning and functionality for each of the inspected classes.\\ 
\subsection{ProductStoreCartAwareEvents.java}
\label{sub:PSCAE}
This java class is composed of two static methods.
The first static method takes a \texttt{HttpServletRequest} and \texttt{HttpServletResponse} as input. The method extracts the \texttt{productStoreId} String parameter from the request and tries to invoke the second static method. Depending on the success or failure of the second method ,	the the first method return either the string "success" or "error"\\
The second static method takes extracted \texttt{productStoreID} String and the \texttt{HttpServletRequest} as input. The method than :
\begin{itemize}
\item returns immediately  if the \texttt{productStoreID} is \texttt{null} or if it equals the \texttt{HttpSession}'s old \texttt{productStoreID}.
\item throws an exception if \texttt{productStoreID} is not related to a valid productStore , if the \texttt{webSite} cannot be found in relation to the request or if \texttt{webSite} exists but does not allow changing of the \texttt{productStoreID}.
\item if the points above are not matched , sets the \texttt{productStoreID} of the \texttt{session} to the one passed as parameter ,clears the old product catalogue and  eventually sets the session's \texttt{currency}, \texttt{locale} and \texttt{time-zone} depending on the \texttt{productStore}. Finally the method creates a new \texttt{shoppingCart} for the session without erasing the old one.
\end{itemize} 
\clearpage
\subsection{ProductDisplayWorker.java}
\label{sub:PDW}
This class is composed of three static methods and a private inner class.
The first method , \texttt{getRandomCartProductAssoc} , receives a \textbf{ServletRequest} and a boolean as input. The methods than extracts the \textbf{ShoppingCart} object from the request and for each item in the cart looks for products that are associated with that product.The associated products found are memorized in a \texttt{cartAssocs} object .From this object all items but three are eliminated randomly. The \texttt{cartAssocs} is then returned.\\
The \texttt{getQuickReorderProducts}   generates \texttt{Map<String, Object>} object containing ordered products. \\The method calls the third static method ,\texttt{prodcutOrderByMao} whose function is to order the products according to the \texttt{Map} passed as parameter. The sorting process uses the static \texttt{sort} method of the Java \texttt{Collections} .\\The private inner class \texttt{ProductByMapComparator} implements \texttt{Comparator<Object>} and is used by the \texttt{Collections.sort} to sort the list.
         